### 2013-10-24 plan.tex
Tweaks.

We propose to create a verified compiler for a language similar to that
discussed in Pottier and Simonet's work\cite{InfoFlowML}.  We will
construct this compiler using the Coq proof assistant\cite{coq?} using
features which allow us to extract a certified compiler.  This will
allow us to take the first step towards a verified compiler for a
language with static information flow types such as Jif\cite{Jif?} or
FlowCaml\cite{FlowCaml?}.

@@

%TODO:
Stuff about the target and source languages we will be supporting.

>>>>

We propose to create a verified compiler for a language similar to that
discussed in Pottier and Simonet's work\cite{InfoFlowML} compiling to a
simple register transfer level (RTL) language.  We will construct this
compiler using the Coq proof assistant\cite{coq?} using features which
allow us to extract a certified compiler.  This will allow us to take
the first step towards a verified compiler for a language with static
information flow types such as Jif\cite{myers1999jflow} or
FlowCaml\cite{simonet2003flow,simonet2003flowmanual}.

@@
